### 2021-06-09 paper/report.tex
Add a few points about testing.

\paragraph{Points to mention}
\begin{itemize}
    \item If anything too optimistic regarding vaccinations
    \item Social structure / conditional block testing in families important (?)
    \item Trump-effect: More testing = more cases true for how long?
    \item Towards the end, total tests go down: Preferences for tests remain the same,
          but infection rates lower \comment[id=HM]{Janos, please fill up}
\end{itemize}

@@

\section{Supplementary Material}

\begin{enumerate}
    \item Model
    \item Data
    \item Identification and Estimation
\end{enumerate}

>>>>

\paragraph{Points to mention}
\begin{itemize}
    \item If anything too optimistic regarding vaccinations
    \item Social structure / conditional block testing in families important (?)
    \item Trump-effect: More testing = more cases true for how long?
    \item Towards the end, total tests go down: Preferences for tests remain the same,
          but infection rates lower \comment[id=HM]{Janos, please fill up}
    \item Actually performed tests increase until May, stay constant during May and then start to drop
    \item This is the combination of the following things:
    \begin{itemize}
        \item time constant willingness to take tests
        \item monotonically increasing availability of tests
        \item endogenous number of situations in which a test should be taken (mainly positive tests of household members)
    \end{itemize}
    \item This is a classic way of modeling in economics: Preferences stay constant
          (and can thus be elicited in just one survey) but outcomes change because
          circumstances change.

\end{itemize}

An important feature of the way we model rapid tests is that the number of actually
performed test is determined endogenously. The number of weekly tests increases until
the end of May and then starts to drop. This is because many  It is determined by the availability of tests,
the individual compliance with testing recommendations and the occurrence of situations
in which a test should be taken.

@@
